Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2019-08-25 anzjs_elections.Rmd
clarification of time-varying restrictions

An identical model specification is used for each of the six elections, with each election modelled separately. This allows the socio-demographic effects to be estimated separately for each election year, facilitating analysis of temporal changes in variable effects. This approach is preferable to using a single longitudinal model because it avoids any concerns of undue bias stemming from incorrectly imposed time-varying restrictions on any variable. Without such restrictions, a pooled cross-sectional model does not yield any distinct advantage over separate cross-sections. The panel approach is avoided because of how frequently electoral boundaries change, noting that electorates with the same name across elections are not guaranteed to represent the same geographical region. Therefore any fixed or random effects models would be difficult to estimate without implementing consistent boundaries, which would require further imputation.

>>>>

An identical model specification is used for each of the six elections, with each election modelled separately. This allows the socio-demographic effects to be estimated separately for each election year, facilitating analysis of temporal changes in variable effects. This approach is preferable to using a single longitudinal model because it avoids imposing any time-varying restrictions on the effect of a variable. To gain any advantage over modelling each election as a separate cross-section, a pooled cross-sectional model would have to force the effects at least some variables to be invariant over time. This would not allow for conclusions to be drawn about how the effects of these variables change over time. Furthermore, the panel approach is avoided because of how frequently electoral boundaries change, noting that electorates with the same name across elections are not guaranteed to represent the same geographical region. Therefore any fixed or random effects models would be difficult to estimate without implementing consistent boundaries, which would require further imputation (of voting information).
